Looking for CDI Bias: WG Production

### 2021-07-07 01-preliminary-WGprod.Rmd
fitting DIF sex to WG comprehension

---
title: "Looking for CDI Bias"
author: "Nathan, George, and Mike"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

>>>>

---
title: "Looking for CDI Bias: WG Production"
author: "Nathan, George, and Mike"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---
